Adopting agile in the large: motivations, success factors and challenges

### 2014-05-03 journal/article.tex
Falling back to old model

>>>>

\subsubsection{Falling back to old model}

In several cases challenges in the transformation resulted in people falling
back to the old model of working.
In some cases it was only a struggle to learn agile practices, but in other
cases the old model displaced agile.
Development work has to go on during the transformation but there will be new
things to learn for the team. Stress caused by the combination of schedule
pressure and much change at once will pull people back to the old way of working
[P11, P18, P38].
Schatz and Abdelshafi tell how even subtle trouble may risk the transformation,
as people will always look for reasons to revert to familiar behavior [P44].
Teams without adequate training were struggling with applying agile practices
correctly, and the challenge the new practices posed made people to abandon them
and return to the ways they know [P6, P49].

In some cases agile was seen as an overhead, and was therefore abandoned. For
instance, as new practices were being introduced there was a decrease
performance, and when teams realized that the benefits are not immediate they
started reverting to the old model [P21].

When a release schedule with fixed deadlines that business required was combined
to agile managers started to behave authoritatively and the self organization of
agile started to break down [P31]. % (Skeptics used this as a sign of that agile can not work)

In one case new senior appointments were changed the management to be less
favorable towards agile, and a waterfall development model started to return
[P12].
